Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
add information of total elapsed time in Fig.11 #17
Explain what is presented by the grey scales Fig. 6 a,b: #8

In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.

@@

The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
All machines tested have an elapsed time of the same magnitude order.

>>>>

In \cref{fig:solar-masks-vf}, we illustrate several aspects of solar masks: \textit{(i)} the solar masks of a building face oriented eastward, showing a discretization of the sun's position in \cref{fig:sm-building-east}; \textit{(ii)} the solar masks for an entire building, representing a detailed discretization of the sun's position throughout the day in \cref{fig:sm-whole-building}; \textit{(iii)} a visualization of the solar mask in the early morning for the city center of Strasbourg in \cref{fig:sm-strasbourg}; and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} used for the computation of view factors and solving heat transfer problems between three building blocks in 2D in \cref{fig:view-factor}.

The grayscale values in each solar mask represent varying levels of solar obstruction for different azimuth and altitude angles.
In these masks, the scale ranges from 0 to 1, where 0 (white) indicates no obstruction and full exposure to sunlight, and 1 (black) represents full obstruction, meaning no sunlight reaches that part of the building face for the given sun position. Intermediate shades of gray indicate partial obstruction, where a portion of sunlight is blocked by surrounding buildings or other urban features.
The level of detail in the solar mask depends on the chosen level of discretization (LOD), as illustrated in \cref{fig:sm-building-east} and \cref{fig:sm-whole-building}.

%In \cref{fig:sm-building-east} (LOD-0), we see a coarser discretization with larger, generalized angular segments, leading to more abrupt transitions between obstructed and non-obstructed areas. In contrast, \cref{fig:sm-whole-building} (LOD-1) provides a finer level of detail, capturing more granular variations in solar accessibility across different sun angles. These masks help quantify the solar exposure of building surfaces over time, which is critical for accurately modeling heat gains and understanding the thermal dynamics of urban environments.

@@

In~\cref{fig:combined-metrics}, the total elapsed time varies from 100 seconds to 1000 seconds in function of the number of nodes.
All machines tested have an elapsed time of the same magnitude order.
